### 2016-03-12 paper/results.tex
figure

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.pdf}
  \caption{}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.pdf}
 \caption{}\label{fig:layered_depthmap_convergence}
\end{figure}

@@

>>>>

%\hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
 \caption{}\label{fig:layered_depthmap_convergence}
\end{figure}

@@

\chen{
  As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings. For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same. There are four parameters in our framework: \textit{the number of threads}, \textit{the number alpha}, \textit{the number beta}, \textit{the number of iterations between each solution sharing}.
}
